%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt]{article}
\usepackage{amsfonts,amssymb,amsmath}
\usepackage{setspace,achicago,graphicx}


\newenvironment{proof}[1][Proof]{\noindent \textbf{#1.} }{\  \rule{0.5em}{0.5em}}

\usepackage[top=.9in, bottom=.9in, left=.9in , right=.9in,letterpaper]{geometry}
%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------
  {\parbox{\textwidth}{\raggedleft \textbf{Fabio Blasutto}\\ % Address line 1
 Place Montesquieu 3/L2.06.01\\ % Address line 2
 1348 Louvain-la-Neuve\\ % Date of birth 
 Belgium \\+32 489545996\\\vspace{0.2cm}}
  {\parbox{1.5\textwidth}{\raggedright March 1, 2019\\
  Department of Economics\\
The University of Chicago\\
1126 E. 59th Street\\
Chicago, IL 60637}}
\vspace{0.5cm}\\
To Whom It May Concern,\\
\vspace{0.5cm}\\
I am a 3rd year Ph.D. student at the \textit{Institut de Recherches \'Economiques et Sociales (IRES)} of UCLouvain, Belgium. My advisors are Prof. David de la Croix and Prof. Fabio Mariani.\vspace{0.3cm}\\
I would hereby like to confirm my interest in joining the PhD school of the University of Chicago as a visiting student for the 2020 winter term.\vspace{0.3cm}\\
My research interest cover family economics, demographic economics and economic history. The first chapter of my dissertation focuses on understanding the different mating behavior observed by education in the USA: single college graduate are relatively less likely to start a cohabitation rather than a marriage compared to the rest of the population, and they are also more likely to experience the transition from cohabitation to marriage. Using a structural dynamic model of partnership choice where agents learn about the quality of their match, I find that for college graduates cohabitation is more of an investment good, used to gather information about the partner that they eventually marry, while for the others informal cohabitation is more of a consumption good, used as a cheap substitute for marriage.\vspace{0.3cm}\\
During my visiting at the University of Chicago I would focus on the development of my first chapter, deepening my understanding about how economic incentives shape the choice between marriage and informal cohabitation. In particular, I plan to study the role of the laws governing separation and divorce: the cost of dissolution and how this is split can not only make more or less costly the transition to singlehood, but they can also  modify the efficiency of risk sharing within the couple through a variation in the degree of commitment. Understanding how different people self select into two types of partnership with different rules governing dissolution is the base for designing welfare enhancing policies. \vspace{0.3cm}\\
In light of the above, I am confident that staying one semester at the University of Chicago would prove extremely insightful for the advancement of my doctoral dissertation. Thank you in advance for your time and consideration.\vspace{0.3cm}\\
Best regards,\vspace{0.5cm}\\
Fabio Blasutto
\end{document}