%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size
\usepackage[italian]{babel}
 \usepackage[T1]{fontenc}
 \usepackage[utf8]{inputenc}
\input{structure.tex} % Include the file specifying document layout
\usepackage{lmodern}
\usepackage{enumitem}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------
\begin{center}
\title{Fabio Blasutto} % Print the main header
\end{center}
%------------------------------------------------

\pagestyle{empty}
\parbox{0.5\textwidth}{ % First block % Enables tabbing
 Université catholique de Louvain\\ % Address line 1
 Place Montesquieu 3/L2.06.01\\ % Address line 2
 1348 Louvain-la-Neuve\\ % Date of birth 
 Belgium % Nationality
}
\hfill % Horizontal space between the two blocks
\parbox[left]{0.5\textwidth}{\raggedleft 

fabio.blasutto@uclouvain.be \\ % Home phone
Born: January 30, 1992 \\
Nationality: Italian \\
+32 489545996  
}
\vspace{0.4cm}
%----------------------------------------------------------------------------------------
%	CURRENT POSITION
%----------------------------------------------------------------------------------------
\section{Current Position}
\textit{PhD Student in Economics}\\
Institut de recherches économiques et sociales (IRES), UCLouvain \\
\textit{Advisors}: Prof. David de la Croix and Prof. Fabio Mariani\\
\vspace{0.2cm}\\
Dissertation chapters: 
\begin{itemize}
\item The Rise of Cohabitation and Unilateral Divorce
(with E. Kozlov) JMP
\item Cohabitation vs Marriage: Mating Strategies by Education in the USA
\item Child and Arranged Marriages in India: How the Caste System Influence the Investment in Education
(with F. Mariani)
\item The Demise of Knowledge Production in Early Modern Italy and The Church's Index\\
(with D. de la Croix)
\end{itemize}
%----------------------------------------------------------------------------------------
%	RESEARCH INTEREST
%----------------------------------------------------------------------------------------
\section{Research Interests}
Demographic and Gender Economics, Family Macro, Development Economics.
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\tabbedblock{
\bf{Exp. 2021}\>\quad PhD in Economics, Université catholique de Louvain (UCLouvain), Belgium
}

\tabbedblock{
	\bf{Sep 2019-}\>\quad Visiting students at Northwestern University \\
	\bf{Feb 2020}
	\>\quad Host: Professor Matthias Doepke
}

\tabbedblock{
\bf{Sep 2016}\>\quad M.Sc. in Economic and Social Sciences (DES), Bocconi University, Italy \\
\>\quad \textit{GPA: 28,86/30. Final grade: 110/110 cum laude}
}
\tabbedblock{
\bf{Sep 2016}\>\quad Joint Degree Program \textit{Research Master in Economics}, Bocconi University, Italy, \\
\>\quad and Université catholique de Louvain (UCL), Belgium\\
\>\quad \textit{GPA: 18/20. Final grade: \textit{Grande Distinction}}
}
%------------------------------------------------

\tabbedblock{
\bf{Sep 2014}\>\quad B.Sc. in Economic and Social Sciences (CLES), Bocconi University, Italy\\
\>\quad \textit{GPA: 28,95/30. Final grade: 110/110 cum laude}
}

%%%%%

\tabbedblock{
\bf{Fall 2014}\>\quad Exchange student at University of California, Irvine Campus, Irvine \\
\>\quad \textit{GPA: 4/4}\\
}

%%%




%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Professional Activities}

\tabbedblock{
\bf{Spring 2015}\>\quad Research Assistance for Prof. Nicola Pavoni (Bocconi University)
}


%----------------------------------------------------------------------------------------
%	TEACHING
%----------------------------------------------------------------------------------------

\section{Teaching}

\tabbedblock{
\bf{2018-2019}\>\quad Teaching assistant at Université catholique de Louvain, Belgium\\
\>\quad Course: Advanced Macroeconomics II (Graduate). Prof. Oikonomou, Rigas
}


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Conferences, Seminars \& Summer Schools}
\begin{itemize}
\item[2020] Macro Lunch Seminar (Northwestern), HD2D Conference (University of Michigan)
\item[2019] III meeting of The Society of Economics of the Household (Lisbon), Doctoral workshop (UCLouvain), ARC Family transformation workshop (UCLouvain), Macro Lunch Seminar (Northwestern), History Lunch Seminar (Northwestern).
\item[2018] XXXIII annual congress of the European Economic Association (Cologne), Summer School on Structural Dynamic Models (Copenhagen), Workshop on Families in Macroeconomics (poster session - Mannheim), Macro Lunch Seminar (UCLouvain), Jamboree of the European Doctorate Program in Quantitative Economics (EUI Florence), ARC Family transformations workshop (UCLouvain).
\item[2017] Jamboree of the European Doctorate Program in Quantitative Economics (Bonn University), Doctoral workshop (UCLouvain), ARC Family transformations workshop (UCLouvain).
\item[2016] Doctoral workshop (UNamur).
\end{itemize}

%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	CONFERENCES, SEMINAR AND SUMMER SCHOOL
%----------------------------------------------------------------------------------------

\section{Fellowship and Awards}
\begin{itemize}
\item PhD Fellowship within the ARC project 15/19-063 on \textit{"Family Transformations: Incentives and Norms"}.
\item PhD Fellowship from the French Speaking community of Belgium:  \textit{FNRS Aspirant}.
\end{itemize}

%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Languages}
Italian (native), English (fluent), French (fluent)


%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{IT skills}
Microsoft office (ECDL Core certification), Stata (Good), Matlab (Good), Eviews (Fair),\\ LaTex(Very Good), Fortran 90 (Very Good), Python (Very Good)
%------------------------------------------------


\end{document}